---
title: "FAIRMODE-Plots"
author: "Christopher Andersen"
date: "2024-03-11"
output: html_document
---

## Data

`FAIRMODE-Plots` contains example data from the `DELTA` tool with observed and modeled concentrations. To create target diagrams and summary reports of this data, we first need to do a few preliminary steps.

First, we source the file `FAIRMODE_Evaluation_functions.R` which contains the necessary functions to load and format the data and create the plots.
We then execute the function `ProgramInitialization()` to load required `R` packages and define important parameters: 

```{r, echo = TRUE, results = 'asis', message = FALSE, warning = FALSE}

source("FAIRMODE_Evaluation_functions.R") 

ProgramInitialization() 

```

Next, we read the `DELTA` tool demo time series data and display the first few rows of the data frame: 

```{r, echo = TRUE, results = 'asis', message = FALSE, warning = FALSE}

UsePrint <- FALSE 

Data <- ReadDELTAData(UsePrint) 

knitr::kable(head(Data))

```

## Target plots

We observe that the data has an hourly time resolution. To proceed from here, we selects one of the four pollutants `NO2`, `O3`, `PM2.5`, or `PM10`, format the data, and compute the quality indicators (the target plot for `NO2` is based on the hourly data so no averages is performed for this pollutant): 

```{r, echo = TRUE, results = 'asis', message = FALSE, warning = FALSE, fig.height = 6.5, fig.width = 6.5}

Pol     <- "NO2" 

Data2   <- FormatDELTAData(Data, Pol, UsePrint) 

StatRep <- FAIRMODEStat(Data2, U_Par, Pol) 

```

We can now specify parameters for the target plot and create the plot, first for `NO2`:  

```{r, echo = TRUE, results = 'asis', message = FALSE, warning = FALSE, fig.height = 6.5, fig.width = 6.5}

PlotPoint  <- 2 # 1: Standard plot. 2: Each station point is uniquely identifiable (only applicable for fewer than app. 100 stations)
OutputDir  <- "FAIRMODE_Evaluation_Plots/" # Name of the relative output directory of plots to be saved
OutputFile <- FALSE # If not FALSE, "OutputFile" overwrites the default file name. If FALSE, the default file name is used
SavePlot   <- FALSE 

TargetPlot(StatRep, PlotPoint, NStations, OutputDir, OutputFile, SavePlot)
```

For `O3`, `FormatDELTAData()` also computes the daily maximum of 8H rolling averages: 

```{r, echo = TRUE, results = 'asis', message = FALSE, warning = FALSE, fig.height = 6.5, fig.width = 6.5}

Pol     <- "O3"

Data2   <- FormatDELTAData(Data, Pol, UsePrint) 

StatRep <- FAIRMODEStat(Data2, U_Par, Pol)

TargetPlot(StatRep, PlotPoint, NStations, OutputDir, OutputFile, SavePlot)
```

For `PM2.5`, `FormatDELTAData()` also computes the daily averages:  

```{r, echo = TRUE, results = 'asis', message = FALSE, warning = FALSE, fig.height = 6.5, fig.width = 6.5}

Pol     <- "PM2.5" 

Data2   <- FormatDELTAData(Data, Pol, UsePrint) 

StatRep <- FAIRMODEStat(Data2, U_Par, Pol)

TargetPlot(StatRep, PlotPoint, NStations, OutputDir, OutputFile, SavePlot)
```

For `PM10`, `FormatDELTAData()` also computes the daily averages:  

```{r, echo = TRUE, results = 'asis', message = FALSE, warning = FALSE, fig.height = 6.5, fig.width = 6.5}

Pol     <- "PM10" 

Data2   <- FormatDELTAData(Data, Pol, UsePrint) 

StatRep <- FAIRMODEStat(Data2, U_Par, Pol)

TargetPlot(StatRep, PlotPoint, NStations, OutputDir, OutputFile, SavePlot)
```

## Summary reports

```{r, echo = TRUE, results = 'asis', message = FALSE, warning = FALSE, fig.height = 6.5, fig.width = 6.5}

Pol     <- "NO2" 

Data2   <- FormatDELTAData(Data, Pol, UsePrint) 

StatRep <- FAIRMODEStat(Data2, U_Par, Pol)

PointSize <- 1.5 # Size of points in each subplot of the summary report

SummaryReport(StatRep, Pol, PointSize, OutputDir, OutputFile, SavePlot)

```

```{r, echo = TRUE, results = 'asis', message = FALSE, warning = FALSE, fig.height = 6.5, fig.width = 6.5}

Pol     <- "O3" 

Data2   <- FormatDELTAData(Data, Pol, UsePrint) 

StatRep <- FAIRMODEStat(Data2, U_Par, Pol)

SummaryReport(StatRep, Pol, PointSize, OutputDir, OutputFile, SavePlot)

```

```{r, echo = TRUE, results = 'asis', message = FALSE, warning = FALSE, fig.height = 6.5, fig.width = 6.5}

Pol     <- "PM2.5"

Data2   <- FormatDELTAData(Data, Pol, UsePrint) 

StatRep <- FAIRMODEStat(Data2, U_Par, Pol)

SummaryReport(StatRep, Pol, PointSize, OutputDir, OutputFile, SavePlot)

```

```{r, echo = TRUE, results = 'asis', message = FALSE, warning = FALSE, fig.height = 6.5, fig.width = 6.5}

Pol     <- "PM10" 

Data2   <- FormatDELTAData(Data, Pol, UsePrint) 

StatRep <- FAIRMODEStat(Data2, U_Par, Pol)

SummaryReport(StatRep, Pol, PointSize, OutputDir, OutputFile, SavePlot)

```