---
title: "FAIRMODE-Plots"
author: "Christopher Andersen"
date: "2024-11-19"
output: html_document
---

## Data

`FAIRMODE-Plots` contains example data from the `DELTA` tool with observed and modeled concentrations. To create target diagrams and summary reports of this data, we first need to do a few preliminary steps.

First, we source the file `FAIRMODE_Evaluation_functions.R` which contains the necessary functions to load and format the data and create the plots. We then execute the function `ProgramInitialization()` to load required `R` packages and define important parameters: 

```{r, echo = TRUE, results = 'asis', message = FALSE, warning = FALSE}

source("FAIRMODE_Evaluation_functions.R") 

ProgramInitialization() 

```

Next, we read the `DELTA` tool demo time series data and display the first few rows of the data frame: 

```{r, echo = TRUE, results = 'asis', message = FALSE, warning = FALSE}

UsePrint <- FALSE 

Data <- ReadDELTAData(UsePrint) 

knitr::kable(head(Data))

```

We observe that the data has an hourly time resolution. To proceed from here, we selects a set of the four pollutants `NO2`, `O3`, `PM2.5`, and `PM10`, together with a start and an end date. Subsequently, we format the data. For `O3`, `FormatDELTAData()` computes the daily maximum of 8H rolling averages while for `PM2.5` and `PM10`, the function computes daily averages. Next, we compute the quality indicators (the target plot for `NO2` is based on the hourly data so no averages is performed for this pollutant): 

```{r, echo = TRUE, results = 'asis', message = FALSE, warning = FALSE, fig.height = 6.5, fig.width = 6.5}

Pol     <- c("NO2", "O3", "PM2.5", "PM10")

Data2   <- FormatDELTAData(Data, PolList = Pol, UsePrint) 

StartDate    <- "2005-01-01" 
EndDate      <- "2006-01-01" 

StatRep <- FAIRMODEAssStat(Data = Data2, StartDate, EndDate, PolList = Pol)

```

## Target plots

We now specify parameters for the target diagrams and create these:  

```{r, echo = TRUE, results = 'asis', message = FALSE, warning = FALSE, fig.height = 6.5, fig.width = 6.5}

Version    <- "DELTA" # Write a version name to be used for target diagram title
PlotPoint  <- 2 # 1: Standard plot. 2: Each station point is uniquely identifiable (only applicable for fewer than app. 60 stations)
OutputDir  <- "FAIRMODE_Evaluation_Plots/" # Name of the relative output directory of plots to be saved
OutputFile <- FALSE # If not FALSE, "OutputFile" overwrites the default file name. If FALSE, the default file name is used
SavePlot   <- FALSE 

TargetPlotAss(StatRepList = StatRep, StartDate, EndDate, PolList = Pol, Version, PlotPoint, OutputDir, OutputFile, SavePlot)
```

Finally, we can do the same to create summary reports:

## Summary reports

```{r, echo = TRUE, results = 'asis', message = FALSE, warning = FALSE, fig.height = 6.5, fig.width = 6.5}

Pol     <- c("NO2", "O3", "PM2.5", "PM10")

Data2   <- FormatDELTAData(Data, PolList = Pol, UsePrint) 

StatRep <- FAIRMODEAssStat(Data = Data2, StartDate, EndDate, PolList = Pol)

Version   <- "DELTA" # Write a version name to be used for target diagram title
PointSize <- 1.5 # Size of points in each subplot of the summary report

SummaryReportAss(StatRepList = StatRep, StartDate, EndDate, PolList = Pol, Version, PointSize, OutputDir, OutputFile, SavePlot)

```